Reproducible Research -- Assigment #1
========================================================
Juan Carlos Guzman
20/Jul/2014

This report shows the solution of homework #1.


## Loading and Preprocessing the Data

We just load the data using read.csv.  Please change the working directory to the location where the data is.
```{r}
setwd("C:/Users/Juan Carlos/Desktop/Reproducible Data/repdata-data-activity")
ds <- read.csv("activity.csv")
summary(ds)
```

## Calculation of Total Number of Steps per Day
```{r}
require(plyr)
ds1 <- ds[complete.cases(ds),]
summary(ds1)
dd2 <- ddply(ds1,~date,summarise,steps=sum(steps))
```

```{r fig.width=7, fig.height=6}
hist(dd2$steps,main = "Average Number of Steps per Day", xlab = "Steps", col="red")
```

The mean and median of steps per day are:

```{r}
mean(dd2$steps)
median(dd2$steps)
```

## Calculation of the Average Daily Activity Pattern
```{r}
require(plyr)
dd3 <- ddply(ds1,~interval,summarise,steps=mean(steps))
```

```{r fig.width=7, fig.height=6}
with(dd3, plot(interval, steps, type = "l",ylab = "Steps", xlab = ""))
```

The following calculation finds the interval with maximum average number of steps.  It specifies the 5-minute interval and the number of steps (i.e., the maximum for any given interval):
```{r}
dd3[which.max(dd3$steps),]
```

##Imputing missing values

The following is the number of rows with "missing values", i.e., the number of rows with "incomplete cases".
```{r}
(dim(ds)-dim(ds1))[1]
```

I filled NA's with zeroes in the data frame (it might be too simple but I was having problems trying to use a more sophisticated value out of the data).  This choice allowed me to continue doing the homework.

```{r}
dd4 <- ds1
dd4$steps <- ifelse(is.na(dd4$steps), 0, dd4$steps)
dd5 <- ddply(dd4,~date,summarise,steps=sum(steps))

```

Following is the mean and median of steps per day of the new data set.  The numbers coincide with the one previously calculated.  I could come back and revise this choice.

```{r}
mean(dd5$steps)
median(dd5$steps)
```

## Calculation of the new graph
the new graph is identical to the previous one.
```{r}
require(plyr)
dd6 <- ddply(dd4,~interval,summarise,steps=mean(steps))
```

```{r fig.width=7, fig.height=6}
with(dd6, plot(interval, steps, type = "l",ylab = "Steps", xlab = ""))
```

dd4$datetype now contains two factors: weekday and weekend, depending on the type of day in date.

```{r}
dd4$datetype <- ifelse(weekdays(as.Date(dd4$date))%in% c('Saturday','Sunday'),"weekend","weekday")
```

The next steps are to generate the graph for each factor.  I will not present it here.



